---
title: "Dynamic report"
output: bookdown::html_document2
params:
  analysis: NA
  known_docs: NA
  model: NA
  qd_path: NA
  qd_doc: NA
---

```{r setup, include=FALSE}
library(handwriter)
library(magick)
```

# Questioned Document

Here is the questioned document (QD).

```{r, echo=FALSE, fig.cap="The questioned document scaled to 100% of the page width", fig.align="center", out.width= "100%"}
qd_image <- magick::image_read(params$qd_path)
qd_image
```

The handwriter R package processed a PNG scan of the QD by

1. Converting the image to black and white
2. Thinning the writing so that it is only one pixel wide
3. Splitting the writing into component shapes called *graphs*
```{r, echo=FALSE, fig.cap="The questioned document split into graphs", fig.align="center"}
handwriter::plotNodes(params$qd_doc)
```

Next, handwriter estimated a writer profile for the QD by assigning its graphs to the cluster template
and counting the number of graphs in each cluster.
```{r, echo=FALSE, fig.cap="The writer profile from the questioned document", fig.align="center"}
handwriter::plot_cluster_fill_counts(params$analysis)
```

# Known Writing Samples
Three known writing samples were collected from each person of interest. The scanned PNG files of the known writing samples are
```{r echo=FALSE}
known_docs <- data.frame("files"=params$known_docs)
knitr::kable(
  known_docs, booktabs = TRUE,
  caption = 'Known writing samples from persons of interest.'
)
```
Each known writing sample was processed with the handwriter package with the same steps as the questioned document:

1. Converting the image to black and white
2. Thinning the writing so that it is only one pixel wide
3. Splitting the writing into component shapes called *graphs*

Next, handwriter estimated a writer profile each person of interest by first assigning the graphs from the known writing samples to the cluster template and counting the number of graphs in each cluster. Then handwriter fit a statistical model, called a Bayesian hierarchical model, to the cluster fill counts of all known writing samples to estimate the true writer profile of each person of interest.
```{r, echo=FALSE, fig.cap="Estimates of the writer profiles of the persons of interest. The error bars show the 2.5% and 9.75% credible intervals.", fig.align="center"}
handwriter::plot_credible_intervals(params$model, facet=TRUE)
```

# Writership Analysis
Using the estimated writer profiles of each person of interest and the writer profile from the QD, handwriter calculates the posterior probability that each person of interest wrote the QD.
```{r, echo=FALSE}
pp <- params$analysis$posterior_probabilities
colnames(pp) <- c("Person of Interest", "Posterior Probability of Writership")
pp <- pp %>% dplyr::mutate(`Posterior Probability of Writership`=paste0(100*`Posterior Probability of Writership`, "%"))

knitr::kable(
  pp, booktabs = TRUE,
  caption = 'The posterior probability that each person of interest wrote the questioned document.'
)
```

